Think deep for reef resilience

### 2025-08-08 paper/paper_draft.qmd
Add section on scenario modelling
Add table quantifying the distances between low and high manag clusters

@@

>>>>

### TODO: Section on scenario modelling

**[TI and BG to flesh out]**

For each GCM, ran 4096 reference scenarios ("counterfactuals")...

@@

```{julia}
#| echo: false
#| warning: false
#| message: false
#| results: asis
#| label: tbl-cluster-cid
#| tbl-cap: Complexity invariant distance (CID) between low and high cluster median timeseries in each management area under each GCM. CID values are calculated for percentage cover timeseries (@fig-gcm-cover-trajectories) and Degree Heating Week (DHW) timeseries (@fig-gcm-dhw-trajectories). Complexity invariant distance represents the euclidean distance between timeseries, corrected by the complexity of the two timeseries. CID values for percentage cover and DHW timeseries are not directly comparable as the timeseries use different units.

using PrettyTables, Markdown
cd("../src")
include("../src/ADRIA/HighResCoralStress/6_quantifying_cluster_differences.jl"); # Quantify low-high cluster differences using CID metric.

io = IOBuffer()

header = ["GCM", "Management area", "CID - cover", "CID - DHW"]
pretty_table(io, distances, backend = Val(:markdown), header = header)

md_string = (String(take!(io)))
Markdown.parse(md_string)
```
